Naming Anonymous JavaScript Functions

### 2011-04-13 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
evaluation and related work sections were updated.

\conferenceinfo{WXYZ '05}{date, City.} 
\copyrightyear{2011} 
\copyrightdata{[to be supplied]}

@@

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

\begin{figure}[htp]

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new, this}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {          // main
10   var foo = new FOO(            
11      function(){                 // main/foo<
12        this.welcome = "Hi!";
13      });
14   var bar = new BAR("GoodBye.");
15   alert(foo.welcome);
16   alert(bar.message);
17 };
18 var FOO = function(){            // FOO<    
19   var instances;
20   return function(initializer){  // FOO
21       instances++;         
22       initializer.apply(this);
23     }
24 }();
25 var BAZ = BAR = function(msg){   // BAR
26   this.message = msg;
27 }
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

@@

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call). A constructor is a regular JavaScript function. Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of one of them({\small\texttt{main}}) correctly. For the second function (line 22), it shows \textit{anonymous}, and for the third function (line 12), it gives a wrong name, {\small\texttt{foo}}. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows {\small\texttt{main}} as the name of last function(line 12) which is the name of its enclosing function.
In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

%Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values. In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The {\small\texttt{this}} value is missed in both views. The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.

@@

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

\section{Building Up Intuition by Example}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We'll ignore nesting of function scopes in the analysis to avoid taking on too much at one time.

\begin{table}
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

\subsection{Case 2: Entry in an Array Literal}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only two have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI:
\begin{verbatim}
_attach: function (el, notifier, delegate) {
  if (Y.DOM.isWindow(el)) {
    return Event._attach([type, function (e) {
         notifier.fire(e);
    }, el]);
  }
}
\end{verbatim}
(The example is nested in more function definitions we do not show here). The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

\subsection{Case 3: Property Assignment With Property Identifier}
This case is the second most common case in the studied projects. Here, we can see why the Closure project is different from other projects in the first case. About 94\% of nameless functions in this project are defined in this way. It seems that the Closure developers follow an internal standard for function objects creation and usage.

Following the model from Case 1, we expect a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression. (This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier). Here is a simple example from the Closure project: 
\begin{verbatim}
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{verbatim}
 These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we can't know the value of \verb|this| while parsing.

@@

\subsection{Case 5: Property Assignment With  Property Name Variable}
Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't (usually) statically compute the string to use as a property identifier.
The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
 name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}. Unlike the previous two cases, we
don't have a specific property name.  Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
\begin{figure*}[htp]
\begin{verbatim}
jQuery.each( "ajaxStart ajaxStop ajaxComplete ajaxError".split(" "), function( i, o ) {
    jQuery.fn[o] = function( f ) {
        return this.bind(o, f);
    };
});
\end{verbatim}
\caption{An example of functions passed as arguments to a function (row 11 in Table~\ref{table:function-types} and (the inner definition) an example of a 
function assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}. The function is from the jQuery library but simplified to fit on the page. }
\label{fig:jQueryEach}
\end{figure*}

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
\begin{verbatim}
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{verbatim}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 8: Assignment to a Variable }
As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
and its internal scopes. Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name works will as the function name.

\subsection{Case 9: Anonymous Functions Immediately Called}
Calling functions objects just after their creations is a common pattern in JavaScript. For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example. 
\begin{figure}[htp]
\begin{verbatim}
Y.ClassNameManager = function () {

 var sPrefix    = CONFIG[CLASS_NAME_PREFIX],
   sDelimiter = CONFIG[CLASS_NAME_DELIMITER];

    return {
       getClassName: Y.cached(function () {
          var args = Y.Array(arguments);
          if (args[args.length-1] !== true) {
              args.unshift(sPrefix);
          } else {
              args.pop();
          }
          return args.join(sDelimiter);
      })
    };
}();
\end{verbatim}
\label{fig:classnamemanager}
\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
\end{figure}

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we can't use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.

\subsection{Case 10: Function Property is Accessed}
In this unusual case a property of the function is accessed directly from the function body. This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.  Here is an example, from ExtJS, reformatted for display here:
\begin{verbatim}
setVisible : function(v, a, d, c, e){
    if(v){
        this.showAction();
    }
    if(a && v){
        var cb = function(){
            this.sync(true);
            if(c){
                c();
            }
        }.createDelegate(this);
   }
   // .....
}
\end{verbatim}
The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|. The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.  This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.

@@

In this case the function body appears in a return statement of another function body. Although this category only includes 2\% of nameless function, proper naming of functions in this class is important. Many constructors are built using this form and therefore the names of these functions appear in object summaries.    Clearly the name of these returned functions is almost the same as the name of the functions that define them. For example, in Fig.~\ref{fig:registerWin} a developer might pick names like \verb|registerWinOnIE| and \verb|registerWinNotOnIE| for the functions returned by the Dojo function \verb|registerWin|.
\begin{figure*}[htbp]
\begin{verbatim}
registerWin: function(targetWindow, effectiveNode){
  // ...
  if(doc){
    if(dojo.isIE){
      ....
      return function(){
        doc.detachEvent('onmousedown', mousedownListener);
        doc.detachEvent('onactivate', activateListener);
        doc.detachEvent('ondeactivate', deactivateListener);
        doc = null;    // prevent memory leak (apparent circular reference via closure)
      };
    }else{
      ....
      return function(){
        doc.removeEventListener('mousedown', mousedownListener, true);
        doc.removeEventListener('focus', focusListener, true);
        doc.removeEventListener('blur', blurListener, true);
        doc = null;    // prevent memory leak (apparent circular reference via closure)
      };
    }
  }
},
\end{verbatim}
\label{fig:registerWin}
\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
\end{figure*}

\subsection{Case 12: Function Passed as an Argument}
Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
For example, see Fig.~\ref{fig:jQueryEach}. The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer. As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.  Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()| seems much less important for naming the function than the property that we initialize with the result of calling the function.
This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.

\subsection{Results of studying examples}
We reached two main conclusions from studying the way anonymous functions are used in the source of the 10 projects we examined. First, we want to try to find the name of the initializer or assignment target that will receive the function object created from a function body.  JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside. Second, these expressions that we focus on may often be simple identifiers, but if they don't we will need to analyze the source of these expressions to extract meaningful summaries. This summary has to balance information against length.

@@

%\subsection{Is it possible to automatically name functions?}
%\subsubsection{Static vs. Dynamic}
% Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?
%\subsubsection{Local vs. Global}
%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime. 
%\subsubsection{Is it possible to automatically name all functions?}
%\subsubsection{Other Challenges}%
% functions pass the name as string, different types of class definitions

>>>>

\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portland, Oregon, USA.} 
\copyrightyear{2011} 
\copyrightdata{[to be supplied]}

@@

\begin{table}%[htp]

\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l |}
  \hline
   Project & Ver. & Description & Total & Named \\ 
  \hline 
   Closure & r683 & Google Web Library & 9195 & 208(2\%) \\ 
  \hline 
   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
  \hline 
   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
  \hline 
   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
  \hline 
   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
  \hline 
   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
  \hline 
   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
  \hline 
   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
  \hline 
   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
  \hline 
   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
  \hline 
   All &  & All Projects & 96008 & 6008(6.3\%) \\ 
  \hline 
  \end{tabular}
  }
\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
\label{js-functions} 
\end{table}

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor. Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

@@

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call). A constructor is a regular JavaScript function. Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.

\begin{figure}%[htp]

\lstset{basicstyle=\scriptsize}
\lstset{emph={Foo,Bar}} %,emphstyle=\bf}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new, this}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {          // main
10   var foo = new Foo(            
11      function(){                 // main/foo<
12        this.welcome = "Hi!";
13      });
14   var bar = new Bar("GoodBye.");
15   alert(foo.welcome);
16   alert(bar.message);
17 };
18 var Foo = function(){            // Foo<    
19   var instances;
20   return function(initializer){  // Foo
21     instances++;         
22     initializer.apply(this);
23   }
24 }();
25 var Baz = Bar = function(msg){   // Bar
26   this.message = msg;
27 }
\end{lstlisting}
\caption{An excerpt of a JavaScript code illustrating anonymous functions. The comments give the results from Sec.~\ref{sec:foc} and these are discussed in Sec.~\ref{sec:examples}}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|. However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. \verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of first function (\verb|main|) correctly. For the second function (line 22), it shows \verb|anonymous|, and for the last function (line 12), it gives a wrong name, \verb|foo|. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows \verb|main| as the name of last function(line 12) which is the name of another function (the enclosing function at line 9). In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.png}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

%Two other pieces of information which are important at function calls are \verb|this}} and argument values. In JavaScript, \verb|this}} like arguments is not defined by lexical scopes but it is bound once the function is called. The \verb|this}} value is missed in both views. The \verb|arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.

@@

\subsection{Context, Package and Function Names}
JavaScript does not support a standard packaging mechanism to be used for modular programming. Scripts are loaded from different files and executed within the same or different global objects. Developers usually use objects at the top level to encapsulate objects, properties and functions from a framework or library. The same mechanism is reused for defining subpackages. As the project size and the number of functions increases, the short function name will not be enough for recognizing the function. The developer also wants the class or the module contains the function. In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.

\section{Building Up Intuition by Example}
\label{sec:intuition}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.  Then we examine each of these cases to think about how we want the functions named. We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.

\begin{table}[htp]
\centering
\scalebox{0.8}{
\renewcommand\arraystretch{2.0}
\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
  \hline
   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
  \hline

@@

\subsection{Case 2: Entry in an Array Literal}
\label{sec:arrayLiteral}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only three have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI \footnote[3]{The example is nested in more function definitions we do not show here.}:
%\begin{verbatim}
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  _attach: function (el, notifier, delegate) {
    if (Y.DOM.isWindow(el)) {
      return Event._attach([type, function (e) {
        notifier.fire(e);
      }, el]);
    }
  }
\end{lstlisting}
%\end{verbatim}
The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

\subsection{Case 3: Property Assignment With Property Identifier}
\label{sec:propid}
This case is the second most common case in the studied projects. Here, we can see why the Closure project is different from other projects in the first case. About 94\% of nameless functions in this project are defined in this way. It seems that the Closure developers follow an internal standard for function objects creation and usage.

Following the model from Case 1, we expect a good name would combine the object name with the property identifier. The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}. Here is a simple example from the Closure project: 
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  this.eventPool_.createObject = function() {
    return new goog.debug.Trace_.Event_();
  };
\end{lstlisting}

 These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small. For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.

@@

\subsection{Case 5: Property Assignment With  Property Name Variable}
Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we cannot (usually) statically compute the string to use as a property identifier.
The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
 name in the cases we examined was generic name like \verb|o| or \verb|item|. Unlike the previous two cases, we
do not have a specific property name.  Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
\begin{figure}[htp]
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  jQuery.each("ajaxStart ajaxStop ajaxComplete ajaxError"
    .split(" "), function( i, o ) {
       jQuery.fn[o] = function( f ) {
         return this.bind(o, f);
       };
  });
\end{lstlisting}
\caption{An example of a function (the inner definition) assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}) and an example of 
functions passed as arguments to a function (row 11 in Table~\ref{table:function-types}). The function is from the jQuery library but simplified to fit on the page. }
\label{fig:jQueryEach}
\end{figure}

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
\label{sec:propexpressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., \verb|condition?"prop1":"prop2"|, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (reformatted to fit in the page):
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{lstlisting}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 8: Assignment to a Variable }
This case is widely used and we expect  developers would expect the function body to get the name of the variable.
As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
and its internal scopes. There are cases in which a variable name is used temporarily, as the function is passed to another function or assigned to an object property. However, in most cases the variable name works well as the function name.

\subsection{Case 9: Anonymous Functions Immediately Called}
Calling function objects just after their creations is a common pattern in JavaScript. For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example. 
\begin{figure}[htp]
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  Y.ClassNameManager = function () {
    var sPrefix = CONFIG[CLASS_NAME_PREFIX],
    sDelimiter = CONFIG[CLASS_NAME_DELIMITER];
    return {
      getClassName: Y.cached(function () {
        var args = Y.Array(arguments);
        if (args[args.length-1] !== true) {
          args.unshift(sPrefix);
        } else {
          args.pop();
        }
        return args.join(sDelimiter);
      })
    };
  }();
\end{lstlisting}
\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
\label{fig:classnamemanager}
\end{figure}

@@

If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use). In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name. To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.

\subsection{Case 10: Function Property is Accessed}
\label{sec:funcprop}
In this unusual case a property of the function is accessed directly from the function body. This case usually happens when one of the predefined functions (i.e., \verb|call, apply,| \verb|bind|) or added functions to the \verb|Function| prototype is called.  Here is an example, from ExtJS, reformatted for display here:
\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
  setVisible : function(v, a, d, c, e){
    if(v){
      this.showAction();
    }
    if(a && v){
      var cb = function(){
        this.sync(true);
          if(c){
             c();
          }
      }.createDelegate(this);
    }
    // .....
  }
\end{lstlisting}
The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|. The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.  This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.

@@

In this case the function body appears in a return statement of another function body. Although this category only includes 2\% of nameless functions, proper naming of functions in this class is important. Many constructors are built using this form and therefore the names of these functions appear in object summaries.    Clearly the name of these returned functions is almost the same as the name of the functions that define them. For example, in Fig.~\ref{fig:registerWin} a developer might pick names like \verb|registerWinOnIE| and \verb|registerWinNotOnIE| for the functions returned by the Dojo function \verb|registerWin|.
\begin{figure}[htbp]

\lstset{basicstyle=\scriptsize}
\begin{lstlisting}[frame=single, language=myLang]
registerWin: function(targetWindow, effectiveNode){
 ...
 if(doc){
  if(dojo.isIE){
   ....
   return function(){
    doc.detachEvent('onmousedown', mousedownListener);
    doc.detachEvent('onactivate', activateListener);
    doc.detachEvent('ondeactivate', deactivateListener);
    doc = null;    
   };
  }else{
   ....
   return function(){
    doc.removeEventListener(
                    'mousedown', mousedownListener, true);
    doc.removeEventListener('focus', focusListener, true);
    doc.removeEventListener('blur', blurListener, true);
    doc = null;   
   };
}}},
\end{lstlisting}
\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
\label{fig:registerWin}
\end{figure}

\subsection{Case 12: Function Passed as an Argument}
Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
For example, see Fig.~\ref{fig:jQueryEach}. The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer. As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.  Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()|) seems much less important for naming the function than the property that we initialize with the result of calling the function.
This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.

\subsection{Results of Studying Examples}
We reached two main conclusions from studying the way anonymous functions are used in the source of the 10 projects we examined. First, we want to try to find the name of the initializer or assignment target that will receive the function object created from a function body.  JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside. Second, these expressions that we focus on may often be simple identifiers, but if they do not we will need to analyze the source of these expressions to extract meaningful summaries. This summary has to balance information against length.

@@

%\subsection{Is it possible to automatically name functions?}
%\subsubsection{Static vs. Dynamic}
% Can we improve the names at runtime?
% function object path in dom model is good candidate for the name but only for persistent objects ?
%\subsubsection{Local vs. Global}
%the object bound to \verb|this}}-depending on the way the function is called-and passed arguments. The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime. 
%\subsubsection{Is it possible to automatically name all functions?}
%\subsubsection{Other Challenges}%
% functions pass the name as string, different types of class definitions
